edgeR

### 2019-08-27 analysis/09_egdeR.Rmd
done with this for now

```{r}
x <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
colData <- read.csv("../metadata/00_colData_characterization.csv", header = T, row.names = 1)
group <- colData$treatment

@@

# To perform quasi-likelihood F-tests:
fit <- glmQLFit(y,design)
qlf <- glmQLFTest(fit,coef=2)
as.data.frame(topTags(qlf))
```

>>>>

```{r}
x <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
colData <- read.csv("../metadata/00_colData_characterization.csv", header = T, row.names = 1)
group <- factor(paste(colData$sex, colData$tissue, colData$treatment, sep = "."))

@@

# To perform quasi-likelihood F-tests:
fit <- glmQLFit(y,design)
qlf <- glmQLFTest(fit,coef=2)
topTags(qlf)
```
